Generate data for NOBA cod ensemble modeling

### 2020-03-20 NOBAcod.Rmd
outline strategy for annual ages

NEXT!!

>>>>

General strategy:

1. add annual age option to run_truth function call, default it to FALSE
  + if true, looks for ANNAGEBIO and ANNAGECATCH in designated directory, error out if missing
  + if true, read these files in addition to existing set rather than replace existing
    + read them in with new load_nc_annage function
    + add them to the output object in addition to existing set
1. write load_nc_annage
  + need to understand annage nc structures
    + if same as others just with full age structure, replace previous nc
    + only numbers output? 
      + how to match with resn and structn for lengths/wts?
      + reconcile with bio parameters such as maturity ogive?
    + only for some groups?
